Plots

### 2025-06-13 src/plots.Rmd
Working on prabhat's feedback 2

    # Plot trend lines for each model
    out <- ggplot(
        df_plot,
        aes(
            x = .data[[group]],
            y = metric,
            color = model_name,
            group = model_name
        )
    ) +
        geom_line(linewidth = 0.75, alpha = 0.4) + 
        geom_line(
            data = df_plot %>%
                group_by(.data[[group]]) %>%
                summarize(
                    metric = mean(metric),
                    model_name = "Mean Across Models"
                ),
            aes(color = model_name),
            se = F,
            linewidth = 1.25
        ) +
        scale_color_manual(values = default_colors) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            legend.title = element_blank(),
            legend.text = element_text(size = legend_text_size),
            legend.position = legend_position, 
            legend.direction = legend_direction,
            legend.box.spacing = legend_spacing,
            plot.title = element_text(size = title_size),
            axis.title.x = element_text(size = x_title_size),
            axis.title.y = element_text(size = y_title_size),
            axis.text.x = element_text(size = x_text_size),
            axis.text.y = element_text(size = y_text_size)
        )
    return(out)

>>>>

    # Plot trend lines for each model
    out <- ggplot(
        df_plot,
        aes(
            x = .data[[group]],
            y = metric,
            color = model_name,
            group = model_name
        )
    ) +
        geom_line(linewidth = 0.75, alpha = 0.4) + 
        geom_line(
            data = df_plot %>%
                group_by(.data[[group]]) %>%
                summarize(
                    metric = mean(metric),
                    model_name = "Mean Across Models"
                ),
            aes(color = model_name),
            se = F,
            linewidth = 1.25
        ) +
        scale_color_manual(values = default_colors) +
        labs(
            title = title,
            x = x_title,
            y = y_title
        ) +
        theme_minimal() +
        theme(
            legend.title = element_blank(),
            legend.text = element_text(size = legend_text_size),
            legend.position = legend_position, 
            legend.direction = legend_direction,
            legend.box.spacing = legend_spacing,
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank(),
            plot.title = element_text(size = title_size),
            axis.title.x = element_text(size = x_title_size),
            axis.title.y = element_text(size = y_title_size),
            axis.text.x = element_text(size = x_text_size),
            axis.text.y = element_text(size = y_text_size)
        )
    return(out)
